### 2021-11-16 thesis/tex/nsiResults.tex
update

\section{Non-Standard Interactions}\label{sec:nsiResults}
\subsection{Constraining the NSI parameters}\label{sec:constraining}
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.

@@

For DeepCore and PINGU, and the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
For DeepCore and PINGU, the median cosine-zenith is $\zreco = 0$, and we allow the event count to rotate around this point.

@@

\begin{figure}
   \begin{center}
      \includegraphics[width=0.8\textwidth]{figures/joint_3D_NO.pdf}
      \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon. $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters not shown in each panel are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{IceCube $\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero.Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
   \end{center}
\end{figure}

@@

\begin{table}
   \centering
   \begin{tabular}{lcc}
      \hline
      Parameter & Best 90\% CL & Best $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &  [-0.054, 0.067] &               [] \\
      $\emt$ &  [-0.029, 0.007] &          [0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] \\
      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] \\
      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] \\
      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013]  \\
      \hline
      \vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Baseline 90\% CL & Baseline $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &   [-0.054, 0.067] &               []\\
      $\emt$  &  [-0.029, 0.007] &          [0.026]  \\
      $\eem$ &    [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &    [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &    [-0.038, 0.048] &  [-0.058, 0.067] \\
      $\emt$ &    [-0.01, 0.006] &  [-0.016, 0.014] \\
      $\eem$ &    [-0.071, 0.086] &  [-0.149, 0.141]  \\
      $\eet$ &   [-0.061, 0.103] &  [-0.131, 0.155] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.01, 0.006] &  [-0.016, 0.014] \\
      \hline
      \vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &    [-0.054, 0.067] &               [] \\
      $\emt$ &    [-0.029, 0.007] &          [0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &     [-0.039, 0.05] &          [-0.06] \\
      $\emt$ &  [-0.011, 0.007] &  [-0.017, 0.015] \\
      $\eem$ &   [-0.082, 0.097] &  [-0.17, 0.16] \\
      $\eet$ &   [-0.067, 0.11] &  [-0.15, 0.17] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.011, 0.007] &  [-0.017, 0.015] \\
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. $\dm[31]$ and $\theta[23]$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
   Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}

@@

\begin{figure}
   \includegraphics[width=0.9\textwidth]{figures/PINGU_2D_all_f0.pdf}
   \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out.}\label{fig:PINGU_2D}
\end{figure}

>>>>

\section{Non-Standard Interactions}\label{sec:nsiResults}
%TODO: add
\subsection{Constraining the NSI parameters}\label{sec:constraining}
In this section, we will constrain the four NSI parameters $\ett$, $\emt$, $\eem$, and $\eet$ by considering the detectors separately as well as jointly.
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin.

@@

%TODO: check that below flows
For DeepCore and PINGU, and the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
The detector's experience an uncorrelated systematic error, which comes from this \emph{muon background}, 
i.e. events misclassified as muons from 
$\nm$ interactions rather than from pion decay. For the DeepCore analysis, we will have to consider this background when calculating the events.
For IceCube events, we scan a higher energy range where the muon background can be neglected. For the PINGU events, the IceCube detector is 
expected to be able to act as a veto for this background. Thus, the error introduced from the muon background is expected by the collaboration 
to be neglible~\cite{PINGUletter}.
The background at PINGU can be considered negligible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$.
For DeepCore and PINGU, the median cosine-zenith is $\zreco = 0$, and we allow the event count to rotate around this point.

@@

\begin{figure}
   \begin{center}
      \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
      \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon. $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters not shown in each panel are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{IceCube $\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero.Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
   \end{center}
\end{figure}

@@

\begin{table}
   \centering
   \begin{tabular}{lcc}
      \hline
      Parameter & Best 90\% CL & Best $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &  [-0.054, 0.067] &               [] \\
      $\emt$ &  [-0.029, 0.007] &          [0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] \\
      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] \\
      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] \\
      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013]  \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Baseline 90\% CL & Baseline $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &   [-0.054, 0.067] &               []\\
      $\emt$  &  [-0.029, 0.007] &          [0.026]  \\
      $\eem$ &    [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &    [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &    [-0.038, 0.048] &  [-0.058, 0.067] \\
      $\emt$ &    [-0.01, 0.006] &  [-0.016, 0.014] \\
      $\eem$ &    [-0.071, 0.086] &  [-0.149, 0.141]  \\
      $\eet$ &   [-0.061, 0.103] &  [-0.131, 0.155] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.01, 0.006] &  [-0.016, 0.014] \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &    [-0.054, 0.067] &               [] \\
      $\emt$ &    [-0.029, 0.007] &          [0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &     [-0.039, 0.05] &          [-0.06] \\
      $\emt$ &  [-0.011, 0.007] &  [-0.017, 0.015] \\
      $\eem$ &   [-0.082, 0.097] &  [-0.17, 0.16] \\
      $\eet$ &   [-0.067, 0.11] &  [-0.15, 0.17] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.011, 0.007] &  [-0.017, 0.015] \\
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. $\dm[31]$ and $\theta[23]$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
   Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}

@@

\begin{figure}
   \includegraphics[scale=0.5]{figures/PINGU_2D_all_f0.pdf}
   \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out.}\label{fig:PINGU_2D}
\end{figure}

### 2021-11-16 thesis/tex/nsiTheory.tex
update

\begin{figure}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{figures/eem_probs.pdf}
        \includegraphics[width=0.9\textwidth]{figures/eet_probs.pdf}
        \caption{Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$. \emph{Top panel:} $\eem = 0.2$. All other NSI parameters are fixed to zero. Instead of the oscillations shifting to the left or right, $\eem$ dampens an oscillation peak for low \si{\GeV}. At \si{\TeV}, the probability is shifted down, just as with $\emt$.
        \emph{Bottom panel:} $\eet = 0.2$. All other NSI parameters are fixed to zero. Here, we see a very weak shifting and a $\nm$ dampening at low \si{\GeV}, and again, no visible effect at \si{TeV} energies. }
        \label{fig:eem_eet_probs}
    \end{center}
\end{figure}

@@

Regarding $\ett$ in Fig.~\ref{fig:eem_eet_probs}, the signal mainly shows in the $\Pamam$ channel as
a weaker resonance dip in the \SI{20}{\GeV} region. Thus, DeepCore/PINGU alone will be used to constrain this parameter.

$\eem$ in Fig.~\ref{fig:eem_eet_probs} shows weak resonance dampening for both $\nm$ and $\anm$.

For $\eet$, we see a similar resonance dampening in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
see the $\eet$ effect in DeepCore/PINGU, but remember that we now have the option to look at the other flavor channels.

>>>>

\begin{figure}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{figures/eem_probs.pdf}
        \includegraphics[width=0.9\textwidth]{figures/eet_probs.pdf}
        \caption{Muon neutrino and antineutrino survival probabilities for
        $\ztrue = -1$. \emph{Top panel:} $\eem = 0.2$. All other NSI parameters are fixed to zero. Instead of the oscillations shifting to the left or right, $\eem$ dampens an oscillation peak for low \si{\GeV}. At \si{\TeV}, the probability is shifted down, just as with $\emt$.
        \emph{Bottom panel:} $\eet = 0.2$. All other NSI parameters are fixed to zero. Here, we see a very weak shifting and a $\nm$ weaker dip at low \si{\GeV}, and again, no visible effect at \si{TeV} energies. }
        \label{fig:eem_eet_probs}
    \end{center}
\end{figure}

@@

Regarding $\ett$ in Fig.~\ref{fig:eem_eet_probs}, the signal mainly shows in the $\Pamam$ channel as
a shallower dip in the \SI{20}{\GeV} region. Thus, DeepCore/PINGU alone will be used to constrain this parameter.

$\eem$ in Fig.~\ref{fig:eem_eet_probs} causes a weaker dip for both $\nm$ and $\anm$.

For $\eet$, we see a similar effect on the dip in $\Pmm$ as we did with $\ett$ for $\Pamam$. Hence, we should be able to 
see the $\eet$ effect in DeepCore/PINGU, but remember that we now have the option to look at the other flavor channels.
